---
title: "EDLD 652 Lab 1"
author: "Havisha Khurana, Merly Klaas, Cassie Malcom"
date: "1/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(tidyverse, rio, here, ggplot2, forcats, stringr, janitor, tidytext)
```

```{r load data, cache = TRUE}
rstats <- import(here("data", "rstats_tweets.rds")) %>%
    as_tibble() %>%
    clean_names()

#rstats
```
## 1. Initial exploration
 * Create histograms and density plots of the display_text_width. 
 * Try at least four different binning methods and select what you think best represents the data for each. 
 * Provide a brief justification for your decision.

```{r}

```

## 2. Look for “plot”
* Search the text column for the word “plot”. 
* Report the proportion of posts containing this word.

```{r}

# count the number of word "plot"
sum(str_count(rstats$text, "plot"))

#proportion of posts containing "plot"
dat <- rstats %>% select(text) %>% 
filter(grepl("plot", text)) %>% 
  count() 
dat
dat / count(rstats) * 100

```
**There are 32,941 words contain the word "plot" in 26,968 posts. The proportion of posts containing the word "plot" is 6.3% of total 429,513 posts.**

## 3. Plot rough draft
* Create the following figure of the 15 most common words represented in the posts.
* Some guidance: You’ll need to drop a few additional words beyond stop words to get a clear picture as above. Consider removing rows where the word is not %in% c("t.co", "https", "http", "rt", "rstats"). This can be a bit tricky (see here for additional help)

```{r clean_data, cache = TRUE}
tweet_words <- rstats %>% 
  select(text) %>% 
  unnest_tokens(word, text) %>% 
  anti_join(stop_words) %>% 
  filter(!word %in% c("t.co", "https", "http", "rt", "rstats")) %>% 
  count(word, sort = TRUE) 
```
```{r basic_plot}
plot <- tweet_words %>% 
  slice(1:15) %>% 
  ggplot(aes(n, reorder(word,n))) +
  geom_col() +
  ylab("word")

plot
```


## 4. Stylized Plot
* Style the plot so it (mostly) matches the below. It does not need to be exact, but it should be close.

```{r}

```
