---
title: "EDLD 652 Lab 1"
author: "Havisha Khurana, Merly Klaas, Cassie Malcom"
date: "1/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(pacman)
```

```{r}
pacman::p_load(tidyverse, rio, here, ggplot2, ggforce, ggridges, ggthemes, colorspace, forcats, stringr, janitor)
```

```{r load data}
rstats <- import(here("data", "rstats_tweets.rds")) %>%
    as_tibble() %>%
    clean_names()

rstats
```

### Initial Exploration 1: Histograms
```{r}

```

### Initial Exploration 2: Density Plots

Let's first plot with the default print setting and see how it looks.

```{r dp_default}
rstats %>% 
  select(display_text_width) %>% 
  ggplot(aes(x = display_text_width))+
  geom_density(color = "cyan4", fill = "cyan3")+
  theme_minimal()+
  labs(
    x = "Characters in Tweet",
    y = "Density"
  )
```

Let's now set four different bin_width.

```{r dp_set}
bin_width = c(2, 5, 10, 50)

for (w in bin_width) {
plot <- rstats %>% 
  select(display_text_width) %>% 
  ggplot(aes(x = display_text_width))+
  geom_density(color = "cyan4", fill = "cyan3", bw = w)+
  theme_minimal()+
  labs(
    x = "Characters in Tweet",
    y = "Density"
  )
print(plot)
}
```

I like the default bin_width as well as bin_widths of 5 and 10. In these three settings, I can clearly tell the graph has three modes at about 80, 130 and 280 characters. Based on the audience, I might choose bin_width of 10 to prevent any confusions about the other little peeks. 

