---
title: "EDLD 652 Lab 1"
author: "Havisha Khurana, Merly Klaas, Cassie Malcom"
date: "1/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(pacman)
```

```{r}
pacman::p_load(tidyverse, rio, here, ggplot2, ggforce, ggridges, ggthemes, colorspace, forcats, stringr, janitor)
```

```{r load data}
rstats <- import(here("data", "rstats_tweets.rds")) %>%
    as_tibble() %>%
    clean_names()

rstats
```
## 1. Initial exploration
 * Create histograms and density plots of the display_text_width. 
 * Try at least four different binning methods and select what you think best represents the data for each. 
 * Provide a brief justification for your decision.

```{r}

```

## 2. Look for “plot”
* Search the text column for the work “plot”. 
* Report the proportion of posts containing this word.

```{r}

```

## 3. Plot rough draft
* Create the following figure of the 15 most common words represented in the posts.
* Some guidance: You’ll need to drop a few additional words beyond stop words to get a clear picture as above. Consider removing rows where the word is not %in% c("t.co", "https", "http", "rt", "rstats"). This can be a bit tricky (see here for additional help)


```{r}

```
## 4. Stylized Plot
* Style the plot so it (mostly) matches the below. It does not need to be exact, but it should be close.

```{r}

```
