---
title: "EDLD 652 Lab 1"
author: "Havisha Khurana, Merly Klaas, Cassie Malcom"
date: "1/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE)
```

```{r}
pacman::p_load(tidyverse, rio, here, stringr, janitor, tidytext)
```

```{r load data, cache = TRUE}
rstats <- import(here("data", "rstats_tweets.rds")) %>%
    as_tibble() %>%
    clean_names()

```
## 1. Initial exploration
 * Create histograms and density plots of the display_text_width. 
 * Try at least four different binning methods and select what you think best represents the data for each. 
 * Provide a brief justification for your decision.

## Initial exploration 1: Histograms

This first histogram is done at the default settings of bin = 30.
```{r}
ggplot(rstats, aes(x = display_text_width)) +
geom_histogram(color = "cyan4", fill = "cyan3") +
  labs(x = "Characters in Tweet")
```

The same histogram is now shown for 4 different bin widths.
```{r}
ggplot(rstats, aes(x = display_text_width)) +
geom_histogram(color = "cyan4", fill = "cyan3", alpha = 0.9, bins = 2) +
  labs(x = "Characters in Tweet")
```

```{r}
ggplot(rstats, aes(x = display_text_width)) +
geom_histogram(color = "cyan4", fill = "cyan3", alpha = 0.9, bins = 5) +
  labs(x = "Characters in Tweet")
```

```{r}
ggplot(rstats, aes(x = display_text_width)) +
geom_histogram(color = "cyan4", fill = "cyan3", alpha = 0.9, bins = 10) +
  labs(x = "Characters in Tweet")
```

**The histogram with bin = 50 appears to show more nuances in the variation, especially in the shorter bars in the right-hand tail. This histogram seems better than the others to show an overview of how many tweets had a certain number of characters.**


```{r}
ggplot(rstats, aes(x = display_text_width)) +
geom_histogram(color = "cyan4", fill = "cyan3", alpha = 0.9, bins = 50) +
  labs(x = "Characters in Tweet")
```

## Initial Exploration 2: Density Plots

Let's first plot with the default bin-width value.

```{r dp_default}
rstats %>% 
  select(display_text_width) %>% 
  ggplot(aes(x = display_text_width))+
  geom_density(color = "cyan4", fill = "cyan3")+
  theme_minimal()+
  labs(
    x = "Characters in Tweet",
    y = "Density"
  )
```

Let's now set four different bin_width.

```{r dp_set}
bin_width = c(0.5, 5, 8, 50)

for (w in bin_width) {
plot <- rstats %>% 
  select(display_text_width) %>% 
  ggplot(aes(x = display_text_width))+
  geom_density(color = "cyan4", fill = "cyan3", bw = w)+
  theme_minimal()+
  labs(
    x = "Characters in Tweet",
    y = "Density",
    subtitle = paste("binwidth = ",w)
  )
print(plot)
}
```


**The density plot with bin widths of 5 and 8 communicate the information well. In both cases, I can clearly tell the graph has three modes at about 80, 130 and 280 characters. Based on the audience, I might choose higher bin_width value of 8 to prevent any confusions about the other little peaks.** 

## 2. Look for “plot”
* Search the text column for the word “plot”. 
* Report the proportion of posts containing this word.

```{r}

# count the number of word "plot"
plot_total <- sum(str_count(rstats$text, "plot"))

#proportion of posts containing "plot"
post_total <- rstats %>% 
  select(text) %>% 
  filter(grepl("plot", text)) %>% 
  count() 

post_prop <- post_total  / count(rstats) * 100

```

**There are `r plot_total` words containing the word "plot" in `r post_total` posts. The proportion of posts containing the word "plot" is `r round(post_prop,2)` of total `r nrow(rstats)` posts.**

## 3. Plot rough draft
* Create the following figure of the 15 most common words represented in the posts.
* Some guidance: You’ll need to drop a few additional words beyond stop words to get a clear picture as above. Consider removing rows where the word is not %in% c("t.co", "https", "http", "rt", "rstats"). This can be a bit tricky (see here for additional help)

```{r clean_data, cache = TRUE}
tweet_words <- rstats %>% 
  select(text) %>% 
  unnest_tokens(word, text) %>% 
  anti_join(stop_words) %>% 
  filter(!word %in% c("t.co", "https", "http", "rt", "rstats")) %>% 
  count(word, sort = TRUE) 
```

```{r basic_plot}
plot <- tweet_words %>% 
  slice(1:15) %>% 
  ggplot(aes(n, reorder(word,n))) +
  geom_col() +
  ylab("word")

plot
```


## 4. Stylized Plot
* Style the plot so it (mostly) matches the below. It does not need to be exact, but it should be close.

```{r}
plot <- tweet_words %>% 
  slice(1:15) %>% 
  ggplot(aes(n, reorder(word,n))) +
  geom_col(fill = "cornflowerblue") +
   geom_vline(xintercept=c(20000, 40000, 60000), color = "gray")+
  labs(x= "Count",
       y = "Word",
       title = "Word frequencies in posts",
       subtitle = "Top 15 words displayed",
       caption = "Data from Mike Kearny, distributed via #tidytuesday") +
  scale_x_continuous(expand = c(0,0) ) + 
  theme (axis.ticks = element_blank())
plot
```

